Simulated Observations of Young Protoplanetary Discs

### 2013-01-22 paper.tex
tweaks to lime mom1 maps

For the purpose of simulating observations the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and is inclined at 30$^\circ$ to edge on. From these observations integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
The simulations were focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 1/100 of the peak emission/absorption value)\newline

@@

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/imageOCS_28-27_30deg_composite_all.eps}
 \label{OCS_all}
 \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map showing clearly differentiated spiral structure in the inner regions of the disc, {\bf Right:} Intensity weighted velocity map}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/imageHCOp_1-0_30deg_composite_all.eps}
 \label{hco+_all}
 \caption{HCO$^+$ 1-0 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
\end{figure*}

>>>>

For the purpose of simulating observations the model was placed at roughly the distance of nearby low-mass star forming regions (100$\,$pc) and is inclined at 30$^\circ$ to edge on. From these observations integrated intensity, intensity weighted velocity and position velocity diagrams through the centre of the model were created.
The simulations were focused upon frequencies within ALMA band 7, selected to give the best trade off between resolution and sensitivity for early ALMA science.
(Note the moment 1 and 0 maps were created by integrating between -12.5 to -0.5 km$\,$s$^{-1}$ and +0.5 to +12.5 km$\,$s$^{-1}$ to avoid being dominated by the contribution from the envelope, this can be seen in some PV diagrams as the strong absorption feature at all positions around zero velocity, moment 1 maps are shown with a cut-off of 3$\sigma$ as defined in section \ref{alma_predicions})\newline

@@

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/imageOCS_26-25_30deg_composite_all.eps}
 \label{OCS_all}
 \caption{OCS 28-27 {\bf Left:} Continuum subtracted integrated intensity map showing clearly differentiated spiral structure in the inner regions of the disc, {\bf Right:} Intensity weighted velocity map}
\end{figure*}

@@

\begin{figure*}
 \includegraphics[width=168mm]{Figures/sim/imageHCOp_3-2_30deg_all.eps}
 \label{hco+_all}
 \caption{HCO$^+$ 3-2 {\bf Left:} Continuum subtracted integrated intensity map, {\bf Right:} Intensity weighted velocity map}
\end{figure*}
